Tropical Andes plant trait data BIEN

### 2023-07-25 code/L0/L0_TropicalAndes_plants_BIEN_traits.Rmd
update summary and species list code

# Write data to csv
```{r}
TropicalAndes_BIEN_traits_path <- file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv") 
write.csv(TropicalAndes_BIEN_traits, file = TropicalAndes_BIEN_traits_path)
```

>>>>

# Extract species list
```{r}
BIEN_trait_SpeciesList <- unique(TropicalAndes_BIEN_occ$scrubbed_species_binomial)
```

# Write data to csv
```{r}
TropicalAndes_BIEN_traits_path <- file.path(output_path,"TropicalAndes_BIEN_plant_traits.csv") 
write.csv(TropicalAndes_BIEN_traits, file = TropicalAndes_BIEN_traits_path)
TropicalAndes_BIEN_species_list_path <- file.path(output_path, "TropicalAndes_BIEN_plant_trait_species.csv")
write.csv(BIEN_trait_SpeciesList, file = TropicalAndes_BIEN_species_list_path)
```
